%\input{作業/preamble_CKL2}
%%\usepackage{wallpaper}                                          % 使用浮水印
%%\CenterWallPaper{0.6}{images/ntpu.eps}                           % 浮水印圖檔
%\begin{document}
%\fontsize{12}{22pt}\selectfont
%\cleardoublepage
%\thispagestyle{empty}
%\setlength{\parindent}{2em}


 
\chapter*{參考文獻}

\begin{enumerate}
\renewcommand{\labelenumi}{[\theenumi]}

\item Aizawa, A.(2003, January). An information-theoretic perspective of tf–idf measures. Information Processing \& Management Volume 39, Issue 1, Pages 45-65.

\item Belgiu, M.(2016,April). Random forest in remote sensing: A review of applications and future directions. ISPRS Journal of Photogrammetry and Remote Sensing Volume 114, Pages 24-31.

\item Bouaziz, A., \& Christel, D. P., \& Pereira, C. C., \& Precioso, F., \& Lloret Patrick.(2014). Short Text Classification Using Semantic Random Forest. Data Warehousing and Knowledge Discovery pp 288–299.

\item Chen, Y., \& Wang, X.(2012). Text feature extraction based on joint conditional entropy. Proceedings of 2012 2nd International Conference on Computer Science and Network Technology.

\item Cortes, C., \& Vapnik, V. (1995). Support-vector networks, Machine Learning volume 20, pages273–297.

\item Eberendu, A. C. (2016, August). Unstructured Data: an overview of the data of Big Data. International Journal of Computer Trends and Technology – Volume 38 Number 1.

\newpage

\item Fazzolari, M., \& Petrocchi, M.(2018,August). A study on online travel reviews through intelligent data analysis. Information Technology \& Tourism volume 20, pages37–58 (2018). 

\item Gretzel, U., \& Kyung, H. Y.(2008,January). Use and Impact of Online Travel Reviews. Information and Communication Technologies in Tourism 2008 pp 35–46.

\item Gretzel, U.(2021). Conceptualizing the smart tourism mindset: Fostering. Utopian thinking in smart tourism development, 1(1), 3–8.

\item Groves, M., \& Mundt, K.(2015). Friend or foe? Google Translate in language for academic purposes. 

\item Huang, Y., \& Wang, R., \& Wei, B., \& Zheng, S. L., \& Chen, M.(2021,July). Sentiment Classification of Crowdsourcing Participants’ReviewsText Based on LDA Topic Model. IEEE Access Volume 9.

\item Koo, C., \& Xiang, Z., \& Gretzel, U., \& Sigala, M.(2021,September). Artificial intelligence (AI) and robotics in travel, hospitality and leisure. Electronic Markets volume 31, pages473–476.

\item Mikolov, T., \& Chen, K., \& Corrado, G., \& Dean, J.(2013, January). Efficient Estimation of Word Representations in Vector Space. arXiv preprint arXiv:1301.3781, 2013.

\item Mikolov, T., \& Surskever, I., \& Chen, K., \& Corrado, G., \& Dean, J.(2013, December). Distributed Representations of Words and Phrases and their Compositionality. Proceedings of the 26th International Conference on Neural Information Processing Systems - Volume 2 Pages 3111–3119.

\newpage

\item Mitra, V., \& Wang, C. J., \& Banerjee, S.(2007,June). Text classification: A least square support vector machine approach. Applied Soft Computing Volume 7, Issue 3, June 2007, Pages 908-914.

\item Mostafa, L(2020). Machine Learning-Based Sentiment Analysis for Analyzing the Travelers Reviews on Egyptian Hotels. Proceedings of the International Conference on Artificial Intelligence and Computer Vision (AICV2020) pp 405–413.

\item Noyum, V. D., \& Mofenjou, Y. P., \& Feudjio, C., \& Göktug, A., \& Fokoue, E.(2021,January). Boosting the Predictive Accurary of Singer Identification Using Discrete Wavelet Transform For Feature Extraction. arXiv - CS - Sound Pub Date : 2021-01-31.

\item Patel, A., \& Meehan, K(2021). Fake News Detection on Reddit Utilising CountVectorizer and Term Frequency-Inverse Document Frequency with Logistic Regression, MultinominalNB and Support Vector Machine. 2021 32nd Irish Signals and Systems Conference (ISSC).

\item Polikar, R.(2012,January). Esemble Learning. Ensemble Machine Learning pp 1–34.

\item Ramos, J.(2003, January). Using TF-IDF to Determine Word Relevance in Document Queries. Department of Computer Science, Rutgers University, 23515 BPO Way, Piscataway, NJ, 08855.

\item Schafer, J. B. \& Frankowski, D., \& Herlocker, J., \& Sen, S.(2007,January). Collaborative Filtering Recommender Systems. The Adaptive Web pp 291–324.

\item Schuckert, M. \& Liu, X., \& Law, R.(2015,August). Hospitality and Tourism Online Reviews: Recent Trends and Future Directions. Journal of Travel \& Tourism Marketing Volume 32, 2015 - Issue 5.

\newpage

\item Song, S., \& Kawamura, H., \& Uchida, J. \& Saito, H.(2019,April). Determining tourist satisfaction from travel reviews. Information Technology \& Tourism volume 21, pages337–367.

\item Stringam, B. B., \& Jr, J. G., \& Vanleeuwen, D. M.(2010,June).Assessing the Importance and Relationships of Ratings on User-Generated Traveler Reviews. Traveler Reviews, Journal of Quality Assurance in Hospitality \& Tourism, 11:2, 73-92.

\item Tang, Y., \& Zhang, Y. Q., \& Chawla, N. V., \&  Krasser, S.(2008,December). SVMs Modeling for Highly Imbalanced Classification. IEEE TRANSACTIONS ON SYSTEMS, MAN, AND CYBERNETICS—PART B: CYBERNETICS, VOL. 39, NO. 1.


\item Wisam, A. Q., \& Musa, M. A., \& Bilal, l. A.(2019, June). An Overview of Bag of Words;Importance, 2019 International Engineering Conference (IEC).

\item Wu, X., \& Kumar, V., \& Quinlan, J. R., \& Ghosh, J., \& Yang, Q., \& Motoda, H., \& McLachlan, G. J., \& Ng, A., \& Liu, B., \& Yu, P. S., \& Zhou, Z. H., \& Steinbach, M., \& Hand, D. J., \& Steinberg, D.(2007,December). Top 10 algorithms in data mining. Knowledge and Information Systems volume 14, pages1–37.

\item Xia, P., \& Zhang, L., \& Li, F.(2015,June). Learning similarity with cosine similarity ensemble. Information Sciences Volume 307, Pages 39-52.

\item Zhao, D., \& Du, N., \& Chang, Z., \& Li, Y.(2017). Keyword extraction for social media short text. 2017 14th Web Information Systems and Applications Conference.

\end{enumerate}
%\end{document}